### 2015-05-31 writing/SNLI paper/abstract.tex
NN eval numbers.

\begin{abstract} 
Understanding entailment and contradiction is  fundamental to understanding natural language, and inference about entailment and contradiction is a valuable testing ground for the development of semantic representations. 
However, research in this area has been dramatically limited by the lack of large-scale resources. 
To address this, we introduce a new freely available corpus of labeled sentence pairs, written by humans in a novel grounded task framing based on image captioning. 
At 570K pairs, it is two orders of magnitude larger than all other resources of its type. 
We also use this corpus to evaluate several natural language inference models. We find that a simple Long Short-Term Memory (LSTM) based model trained on our corpus not only performs competitively on our own evaluation set, but also achieves the best reported performance for a neural network model on an existing natural language inference benchmark.
\end{abstract}

>>>>

\begin{abstract} 
Understanding entailment and contradiction is  fundamental to understanding natural language, and inference about entailment and contradiction is a valuable testing ground for the development of semantic representations. 
However, research in this area has been dramatically limited by the lack of large-scale resources. 
To address this, we introduce a new freely available corpus of labeled sentence pairs, written by humans in a novel grounded task framing based on image captioning. 
At 570K pairs, it is two orders of magnitude larger than all other resources of its type. 
We also use this corpus to evaluate several natural language inference models. We find that a simple Long Short-Term Memory (LSTM) based neural network model trained on our corpus performs well on our evaluation set and achieves the best reported performance for a neural network model on an existing natural language inference benchmark.
\end{abstract}

### 2015-05-31 writing/SNLI paper/entailment_eval.tex
NN eval numbers.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{75?} & \t{72?} \\	
\t{100d LSTM RNN}            & \t{81.4?} & \t{78.0?} \\
% \t{100d TreeRNN}            & \t{69?} & \t{69?} \\
% \t{50d TreeRNTN}            & \t{61?} & \t{60?} \\
% \t{100d LSTM TreeRNN}            & \t{72?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on our training and test sets for each model.
\todo{Replace with final numbers}
}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d LSTM RNN (random init.)}            & \t{100} & \t{71.3} \\
% From: ~/quant/transfer-sick-only-l0.0001-dim50-ed200-td3-pen100-do0.9-0.9-ws1-par0-comp2-cdim1/
\t{100d LSTM RNN (transfer init.)}            & \t{100?} & \t{80.8?} \\
% From: ...
\hline
\end{tabular}
\end{center}

\caption{\label{tab:transferresults}
The performance (\% accuracy) of an LSTM RNN model on SICK under both a random initialization and a transfer initialization copied from a model trained on our corpus.  \todo{Final numbers.}} 
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79.3} & \t{75.3} \\
% scr/snlirc3d-snlirc3-only-l0.0001-dim100-ed300-td3-pen200-do0.9-0.9-co3-comp-1-dp1-gc5-lstminit5/stat_log
% 290500, dev 76.4, mostly converged, but check

\t{100d RNN}            & \t{73.4} & \t{71.8} \\	
% scr/snlirc3d-snlirc3-only-l0.0001-dim100-ed300-td3-pen200-do0.9-0.9-co3-comp3-dp1-gc5-lstminit5/stat_log
% 307500, dev 71.744,

\t{100d LSTM RNN}            & \t{84.8} & \b{78.0} \\
% scr/snlirc3d-snlirc3-only-l3e-05-dim100-ed300-td3-pen200-do0.95-0.95-co3-comp2-dp1-gc5-lstminit5/stat_log
% 372000, dev 79.039

% \t{100d TreeRNN}            & \t{69?} & \t{69?} \\
% \t{50d TreeRNTN}            & \t{61?} & \t{60?} \\
% \t{100d LSTM TreeRNN}            & \t{72?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on our training and test sets for each model.
}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d LSTM RNN (random init.)}            & \t{100} & \t{71.3} \\
% From: ~/quant/transfer-sick-only-l0.0001-dim50-ed200-td3-pen100-do0.9-0.9-ws1-par0-comp2-cdim1/

\t{100d LSTM RNN (transfer init.)}            & \t{99.9} & \b{80.8} \\
% From: ~/quant/transfer5-sick-only-transfer-l0.0001-dim100-ed300-td3-pen200-do0.95-0.95-ws3-adi0-comp2-cdim1/stat_log
\hline
\end{tabular}
\end{center}

\caption{\label{tab:transferresults}
The performance (\% accuracy) of an LSTM RNN model on SICK under both a random initialization and a transfer initialization copied from a model trained on our corpus.} 
\end{table}

### 2015-05-31 writing/SNLI paper/intro.tex
NN eval numbers.

In this paper, we use this corpus to evaluate a wide variety of models
for natural language inference, including rule-based systems, simple
linear classifiers, and compositional neural networks. We find that
a neural network model which uses a Long Short-Term Memory network (LSTM; 
\citealt{hochreiter1997long}) to represent sentence meaning achieves the best
performance, and we validate that strong performance by showing that
a model trained on our data can be successfully adapted to an existing
NLI challenge task, yielding the best reported performance for a neural network model.

>>>>

In this paper, we use this corpus to evaluate a wide variety of models
for natural language inference, including rule-based systems, simple
linear classifiers, and compositional neural networks. 
We find that two models achieve comparable performance: a feature-rich
classifier model and a neural network model which uses a Long Short-Term Memory network (LSTM; 
\citealt{hochreiter1997long}) to represent sentence meaning. We further evaluate the LSTM model
by taking advantage of its ready support for transfer learning, and show that it can be adapted to an existing
NLI challenge task, yielding the best reported performance for a neural network model.
